## README

The NHDPlusERG R package uses the **NHDPlus** database to extract data from COMID useful to **ERG**. This package uses functions from package *nhdplusTools*, cited below.

### dependencies

This package requires R packages *devtools, nhdplusTools, ggplot, and sf*

### directions

install and load devtools:

```{r}
install.packages("devtools")
library(devtools)
```

install NHDPlusERG and load NHDPlusERG with dependencies:

```{r}
install_github("kentcod/NHDPlusERG")
library(NHDPlusERG)
library(nhdplusTools)
library(sf)
library(ggplot2)
library(tidycensus)
```

### Functions

functions found in this package match COMID to FIPS county code and map said relationship. Functions also extract population demographics from ACS using county code.

for additional info, consult help menu for information on each function

```{r}
?COMID.FIPS
?map.FIPS
?COMID.demo
```

### References

Blodgett, D., Johnson, J.M., 2022, nhdplusTools: Tools for Accessing and Working with the NHDPlus, <https://doi.org/10.5066/P97AS8JD>
Walker, K., 2021, tidycensus: Load US Census Boundary and Attribute Data as 'tidyverse' and 'sf'-Ready Data Frames. R package version 1.2.3. Retrieved from https://CRAN.R-project.org/package=tidycensus
